High-Fidelity Counterfactual Explanations through Conformal Prediction

### 2023-04-22 notebooks/mnist.qmd
getting somewhere

```{julia}
# Model parameters:
epochs = 100
batch_size = minimum([Int(round(n_obs/10)), 128])
n_hidden = 50
activation = Flux.swish
builder = MLJFlux.@builder Flux.Chain(

@@

# Joint Energy Model:
𝒟x = Uniform(-1,1)
𝒟y = Categorical(ones(output_dim) ./ output_dim)
sampler = ConditionalSampler(
    𝒟x, 𝒟y, 
    input_size=(input_dim,), 
    batch_size=10
)
jem = JointEnergyClassifier(
    sampler;
    builder=builder,
    batch_size=batch_size,
    finaliser=x -> x,
    loss=Flux.Losses.logitcrossentropy,
    jem_training_params=(
        α=α,verbosity=10,
        # use_gen_loss=false,
        # use_reg_loss=false,
    ),
    sampling_steps=20,
    epochs=epochs,
)

@@

```{julia}
𝒟x = Uniform(-1,1)
𝒟y = Categorical(ones(K) ./ K)
sampler = UnconditionalSampler(𝒟x; input_size=(D,))
conditional_sampler = ConditionalSampler(𝒟x, 𝒟y; input_size=(D,))
opt = ImproperSGLD()
n_iter = 100
```

@@

# ECCCo:
λ=[0.0,1.0,10.0]
temp=0.01

>>>>

```{julia}
# Model parameters:
epochs = 100
batch_size = minimum([Int(round(n_obs/10)), 128])
n_hidden = 128
activation = Flux.swish
builder = MLJFlux.@builder Flux.Chain(

@@

# Joint Energy Model:
𝒟x = Uniform(-1,1)
𝒟y = Categorical(ones(output_dim) ./ output_dim)
sampler = ConditionalSampler(
    𝒟x, 𝒟y, 
    input_size=(input_dim,), 
    batch_size=1
)
jem = JointEnergyClassifier(
    sampler;
    builder=builder,
    batch_size=batch_size,
    finaliser=x -> x,
    loss=Flux.Losses.logitcrossentropy,
    jem_training_params=(
        α=α,verbosity=10,
        # use_gen_loss=false,
        # use_reg_loss=false,
    ),
    sampling_steps=20,
    epochs=epochs,
)

@@

```{julia}
Random.seed!(1234)

# Set up search:
factual_label = 9
x = reshape(counterfactual_data.X[:,rand(findall(predict_label(M, counterfactual_data).==factual_label))],input_dim,1)
target = 4
factual = predict_label(M, counterfactual_data, x)[1]
γ = 0.5
T = 250

@@

# ECCCo:
λ=[0.1,0.1,0.1]
temp=0.1
